Chlorophylla

### 2019-02-27 Chlorophyll_a .Rmd
A rough fix to create daily cholorphyl-a data from the 8 day data

The aim of this script is to extract the chlorophyll a netCDF files and convert it to CSV. The chlorophylla data was obtained from MODIS Aqua. The aim of working with this chlorophyll a data is to examine how the chlorophyll a  concentration varies with upwelling.

```{r}
library(ncdf4)
library(data.table)
library(tidyverse)
library(reshape2)
library(plyr)
library(lubridate)
library(stringr)
library(doMC); doMC::registerDoMC(cores = 4)
library(ggpubr)
library(fasttime)
library(FNN)

@@

Chlorophyll-a data are 8day composites. In order to compare the chlorophyll concentration with upwelling events, take 8days, take the average. This is one value. Repeat this so what i have a time series with chlorophyll-a data every 8days.

@@

daily_chloro_data <- MODIS_Chloro %>%
  dplyr::mutate(date = as.Date(date)) %>% 
  mutate(month = month(date),
         day = day(date),
         year = year(date)) %>% 
  dplyr::group_by(lon, lat, day, month, year) %>% 
  dplyr::summarise(chloro = mean(chloro, na.rm = TRUE))

@@

daily_chloro_match <- daily_chloro_data %>%
  unite(col = combi, lon, lat, sep = "/", remove = F) %>%
  filter(combi %in% pixel_match$combi)

daily_chloro_match_sites <- daily_chloro_match %>%
  left_join(pixel_match, by = c("combi", "lon", "lat", "month", "day", "year")) 
```

>>>>

The aim of this script is to extract the chlorophyll a netCDF files and convert it to CSV. The chlorophylla data were obtained from MODIS Aqua. The aim of working with these chlorophyll a data is to examine how the chlorophyll a concentration varies with upwelling.

```{r}
library(ncdf4)
library(data.table)
library(tidyverse)
library(reshape2)
library(plyr) # Never load plyr when also loading the tidyverse. It causes a lot of conflicts.
library(lubridate)
library(stringr)
library(doMC); doMC::registerDoMC(cores = 4)
library(ggpubr)
library(fasttime)
library(FNN)
library(heatwaveR)

@@

Chlorophyll-a data are 8 day composites. In order to compare the chlorophyll concentration with upwelling events, take 8 days, take the average. This is one value. Repeat this so what I have a time series with chlorophyll-a data every 8 days.

@@

@@

daily_chloro_match <- MODIS_Chloro %>%
  unite(col = combi, lon, lat, sep = "/", remove = F) %>%
  filter(combi %in% pixel_match$combi)

# With the chloro pixels filter, it is now faster to create the daily data
daily_chloro_data <- daily_chloro_match %>%
  dplyr::mutate(date = as.Date(date)) %>% 
  dplyr::group_by(combi, lon, lat, date) %>% 
  dplyr::summarise(chloro = mean(chloro, na.rm = TRUE)) %>% 
  dplyr::group_by(combi, lon, lat) %>% 
  tidyr::nest() %>% 
  dplyr::mutate(clims = purrr::map(data, ts2clm, x = date, y = chloro,
                       climatologyPeriod = c("2002-07-13", "2018-12-04"), # This doesn't mean anything, but the function needs it to work
                       maxPadLength = 8)) %>% # Adjust maxPadLength = X for longer interpolation
  dplyr::select(-data) %>% 
  tidyr::unnest() %>% 
  select(-doy, -seas, -thresh)

ggplot(daily_chloro_data, aes(x = date, y = chloro)) +
  geom_line() +
  facet_wrap(~combi, ncol = 1)

# daily_chloro_match_sites <- daily_chloro_data %>%
#   left_join(pixel_match, by = c("combi", "lon", "lat", "month", "day", "year")) 
```
